### 2020-11-13 about/vita.tex
Updated vita

\footline{\phantom{\datethis}\hss\folio\hss\datethis}  % \phantom for centering

@@

@@

Analysis and design of algorithms, analysis of random discrete structures, combinatorics, group theory,
programming language theory and design, compilers.

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$0.40 in Knuth reward cheques.
\medbreak

>>>>

% \footline{\phantom{\datethis}\hss\folio\hss\datethis}  % \phantom for centering

@@

\leftright{\bf \'Ecole Secondaire Beaumont Composite High School}{\bf September 2014 -- June 2015}
\leftright{\sl Tutor}{\sl Beaumont, AB, Canada}
\smallskip
Tutored various students in grades 4 through 11 in chemistry, physics, math, and French.
\medbreak

@@

Analysis and design of algorithms, analysis of random discrete structures, enumerative combinatorics,
additive combinatorics, group theory,
programming language theory and design, compilers.

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\medbreak

\rightline{\eightrm \datethis}
